\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage[russian]{cleveref}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Anastasia Ciaica} & Email : \href{mailto:chaika.a@phystech.edu}{chaika.a@phystech.edu}\\
  Moscow, Russia & Mobile : \href{+79776121603}{+79776121603} \\
  & \href{https://github.com/ciaica-anastasia}{https://github.com/ciaica-anastasia} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
   \item{
      \textbf{Moscow Institute of Physics and Technology (MIPT)}} \hfill{Moscow, Russia}\\
      {Bachelor of Science in Computer Science}\hfill{Sep 2018 - Present}\\
      {Phystech School of Applied Mathematics and Informatics}
      
  \resumeSubHeadingListEnd

\section{Experience}

  \resumeSubHeadingListStart
  
  \item{
      \textbf{Amdaris Company}} \hfill{Chisinau, Moldova}\\
      {\emph{Full Stack Web Developer Intern}} \hfill{Feb - May 2021} \\ {Gained hands-on experience in building enterprise MVC applications, using ASP.NET Core \\ Framework, Entity Framework Core, ASP.NET Identity, React and Material Design.} \\
  
   \item{
      \textbf{Allied Testing Company}} \hfill{Chisinau, Moldova}\\
      {\emph{QA Automation Engineer}} \hfill{Nov 2020 - Apr 2021} \\ {Developed and maintained Web API and UI test automation framework to drive quality\\ and efficiency in accordance with client’s software specifications, involving usage of Maven \\ and following libraries: TestNG, JUnit, Cucumber, Selenium, Apache POI, Apache \\ HttpClient, XStream and Jackson. Identified and reported product defects via Jira. \\ Measured system performance using JMeter and Load Runner. } \\

  \resumeSubHeadingListEnd

\section{Projects}

\resumeSubHeadingListStart
		\item{
   \href{https://github.com/atp-mipt/xylophone2}{\textbf{Xylophone}} { \\Worked in a team on an open source library for generating Excel reports from raw data in XML format using a descriptor(a file describing data traversal) and a report template. Added new features for reading data and descriptor in JSON and YAML format, covered with unit tests.}
   
   Tools: Java, JUnit, Jackson.
   }
   
         \item{
   \href{https://github.com/ciaica-anastasia/.Net-Internship}{\textbf{eLearning School}} { \\Built an ASP.NET Core Web API with Entity Framework Core, authentication, and CRUD operations. Implemented Clean Architecture and CQRS pattern with MediatR. Business logic of the project -- an online school of foreign languages with the ability to authenticate as an administrator or a student to view and select classes.}
   
   Tools: C\#.
   }
   
   \item{
   \href{https://github.com/ciaica-anastasia/Optimal-Scheduling}{\textbf{Optimal Scheduling}} { \\Found an optimal solution for the nurse scheduling problem (NP-hard) - the operations research problem of finding an optimal way to assign employees to shifts, using simulated annealing algorithm. Took into account hard (employee coverage, prohibited working patterns) and soft (individual work preferences) constraints. } 
   
   Tools: Python.
   }

          \item{
   \href{https://github.com/ciaica-anastasia/Microshell}{\textbf{Microshell}} { \\Developed a UNIX Shell, which involved parsing command line arguments, spawning processes, replacing user contexts, implementing I/O redirection, waiting for spawned processes, listing files in directories, directory traversal, pattern matching, obtaining information about spawned processes.}
   
   Tools: C++.
   }
          \item{
   \href{https://github.com/ciaica-anastasia/TCP-Client-Server}{\textbf{TCP Client-Server}}{\\ Built a TCP client-server program, where clients have the opportunity to get their message history and the message history of any other client.}
   
   Tools: C.
   }
   
\resumeSubHeadingListEnd


\section{Skills}
\resumeSubHeadingListStart
	\item {\textbf{Programming Languages}{: Java, C\#, C++, C, SQL, Python, \LaTeX. }}
	\item {\textbf{Technologies and Tools}}{: Maven, Java libraries (TestNG, JUnit, Cucumber, Selenium, Apache POI, Apache HttpClient, XStream, Jackson), ASP.NET Core, EF Core, Postman, Fiddler,  JMeter, Load Runner, VCS, 3D Printing.}
	\item {\textbf{Languages}{: Russian (Native), English (Advanced, TOEFL iBT Score 103), Romanian (Advanced), Spanish (Beginner), German (Beginner).}}
 \resumeSubHeadingListEnd



\section{Achievements and Extracurricular Activities}

  \resumeSubHeadingListStart

\item{
      \textbf{MIPT Freshmen Mentor}} \hfill{Moscow, Russia}\\
      {Supervised a group of freshmen, engaged in their adaptation to university life.}\hfill{Sep 2020 - June 2021}\\
      
   \item{
      \textbf{Online English Teacher}} \hfill{}\\
      {Taught English to students of different levels and ages, TOEFL exam preparation.}\hfill{Apr 2020 - Nov 2020}\\
      
      \item{
      \textbf{Children's Health Camp "SPARTA"}} \hfill{Bulgaria}\\
      {\emph{Senior Camp Counselor}}\hfill{Summer 2018, 2019}\\
      {Worked with children of different ages and backgrounds (including children from\\ orphanages), as well as fully coordinated the work of all counselors and organized\\ camp-wide games and events involving more than 100 children and employees.}

   \item{
      \textbf{AYFN Summer Japan Experience Program}} \hfill{Japan}\\
      {Immersed in the culture and science of Japan together with other students from around}\hfill{Summer 2019}\\
      {the world.}
      
   \item{
      \textbf{Step Aerobics University Team}} \hfill{Moscow, Russia}\\ 
      {Prize-winner of the Step Aerobics Moscow Cup.} \hfill{2018}\\  
      
   \item{
      \textbf{Future Leaders Exchange (FLEX) Program}} \hfill{USA}\\
      {Learned about the people and culture of the United States through international exchange}\hfill{2016 - 2017}\\
      {while attending a U.S. high school and living with a U.S. host family.}
      
   \item{
      \textbf{The President's Volunteer Service Award}} \hfill{USA}\\
      {Completed 164 hours of community service.}\hfill{2017}\\
      
   \item{
      \textbf{Organization of fundraising projects}} \hfill{USA}\\ 
      {Having teamed up with the students from 18 countries, I organized my own fundraising}\hfill{2017}\\
      {project “Multicultural Fair”, whose outcome in the amount of \$400 covered part of the cost of\\ treatment of a cancer patient.}
     
  \resumeSubHeadingListEnd
  
\end{document}